---
title: "Regression 2, Regression 3, and Regression 4 "
author: "Nam Tran"
date: "2022-08-08"
output: word_document
---

Import some necessary package for the project

```{r}
pacman::p_load(pacman, tidyverse, magrittr, psych, skimr, zoo, data.table, sqldf, parallel, plyr, lubridate, broom, car, tictoc)
```

Import the data

```{r}
df <- read.csv("stock_data3.csv", stringsAsFactors = T) %>% as_tibble()
```

```{r}

df %<>% select(-X)

```


Rearrange Column Headers

```{r}
df %<>%
  select(date,
         PERMNO,
         TICKER,
         COMNAM,
         Sector,
         PRC,
         MKT_CAP,
         SHROUT,
         ind_ret,
         EFFR,
         mkret)
```

Create some columns to facilitate the dual beta model

```{r}
# Create a daiy market cap
df <- sqldf("SELECT *,
      sum(MKT_CAP) over(partition by date, Sector) as Sector_MKTCAP
      FROM df
      ") %>% as_tibble()

# Create a market_cap share column, which is show the market cap proportion of each individual's stock in a Sector
# Create a Return_Weighted variable, which is the daily weighted return of a stock in a sector.

df %<>% mutate(MKTCAP_SHARE = MKT_CAP/Sector_MKTCAP, # Market cap Percent Of individual stock in an Sector
               Return_Weighted = ind_ret * MKTCAP_SHARE) 

# Create a Daily_Sector_Return
df <- sqldf("SELECT *, 
      sum(Return_Weighted) over(partition by date, Sector) as Daily_Sector_Return 
      FROM df")

# format the date variable and create a year column

df %<>% mutate(date = ymd(date),
               year = year(date))

# Most important variables 

df %<>% mutate(excess_ret = ind_ret - EFFR,
               mket_prem = mkret - EFFR,
               sector_prem = Daily_Sector_Return - EFFR
               )
df %<>% mutate(PERMNO = as.factor(PERMNO)) 
```

-   Create an estimation dataset, from beginning 2016 to end 2018

```{r}
estimation <- df %>% filter(year %in% c(2016, 2017, 2018))
```

# Run the Dual Beta Regression

-   fit_stat 1 will include the alphas, betas, and their corresponding p values

```{r}

fit_stat1 <- estimation %>% 
  nest(data = -PERMNO) %>% 
  mutate(model = map(data, ~lm(excess_ret~mket_prem + sector_prem, data=.)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied)

```

-   fit_stat2 will include the model's adjusted R squared and its p value

```{r}
fit_stat2 <- estimation %>% 
  nest(data = -PERMNO) %>% 
  mutate(model = map(data,~lm(excess_ret ~ mket_prem + sector_prem, data =.)),
         tidied = map(model, glance)) %>% 
  unnest(tidied)
```

-   Round the output and remove some unnecessary columns

```{r}
fit_stat1 %<>% mutate_if(is.numeric, round, digits = 4)
fit_stat1 %<>% select(-c(data, model, std.error, statistic)) 
```

```{r}
fit_stat2 %<>% mutate_if(is.numeric, round, digits = 4)
fit_stat2 %<>% select(PERMNO, adj.r.squared, p.value)
```

Join two outputs together

```{r}
est_output <- join(fit_stat1, fit_stat2, by = "PERMNO")
est_output[,6] <- NULL #Remove the Null column
```

*Plot Statistic outputs*

```{r}
est_output %>% ggplot() +
  geom_density(aes(x = estimate, col = term), data = est_output) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta", "Sector Premium")) + 
  theme(panel.background = element_blank()) +
  xlab("Coefficient") + 
  ylab("Density") +
  ggtitle("Dual Beta Model Distribution of Coefficients")
```

```{r}
est_output %>% ggplot() +
  geom_density(aes(x = p.value, col = term), data = est_output) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta", "Sector Premium")) + 
  theme(panel.background = element_blank()) +
  xlab("P-Value") + 
  ylab("Density") +
  ggtitle("Dual Beta Model Distribution of Coefficient's P-Value")
```

```{r}
est_output %>% ggplot() +
  geom_point(aes(y= p.value, x = PERMNO, col = term), data = est_output, alpha = 0.8) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta", "Sector Premium")) + 
  theme(panel.background = element_blank(),
        legend.key = element_blank()) +
  xlab("PERMNO") + 
  ylab("P-Value") +
  ggtitle("Dual Beta Model Distribution of Coefficient's P-Value")
```

```{r}
est_output %<>% mutate(Alpha = NA,
                      Beta = NA,
                      Sector_Prem = NA) 

# Fill variable Alpha

for (i in 3:nrow(est_output)){
  est_output$Alpha[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    estimate[i-2], NA))}

# Fill variable Beta

for (i in 3:nrow(est_output)){
  est_output$Beta[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    estimate[i-1], NA))
}

# Fill variable Sector_Prem

for (i in 3:nrow(est_output)){
  est_output$Sector_Prem[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    estimate[i], NA))
}

est_output %<>% mutate(Alpha_pval = NA,
                      Beta_pval = NA, 
                      Sector_Prem_pval = NA)

# Fill variable Sector_Prem_pval 

for (i in 3:nrow(est_output)){
  est_output$Sector_Prem_pval[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    p.value[i], NA))}

# Fill variable Beta_pval 

for (i in 3:nrow(est_output)){
  est_output$Beta_pval[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    p.value[i-1], NA))}
  
# Fill variable Alpha_pval

for (i in 3:nrow(est_output)){
  est_output$Alpha_pval[i] = with(est_output,
                             ifelse(PERMNO[i] == PERMNO[i-1] & PERMNO[i] == PERMNO[i-2],
                                    p.value[i-2], NA))}

```

*Remove some columns and rows*

```{r}
est_output %<>% 
  filter(term == "sector_prem") %>% 
  select(-c(term, estimate, p.value)) %>% 
  dplyr::rename( 
      Reg2_ARS = adj.r.squared, 
      Reg2_B0 = Alpha,
      Reg2_B1 = Beta,
      Reg2_B2 = Sector_Prem,
      Reg2_P1 = Beta_pval,
      Reg2_P0 = Alpha_pval,
      Reg2_P2 = Sector_Prem_pval
)

```

Join this output with the Basic capm output to get the tickers and sector

```{r}
dt <- read.csv("modified_output.csv")
est_output <- sqldf("SELECT e.*, d.tic, d.Sector
      FROM est_output as e
      JOIN dt as d
      ON e.PERMNO = d.PERMNO") %>% as_tibble() %>% 
  select(PERMNO, tic, Sector, everything()) 
```

Export the output

```{r}
write.csv(est_output, "est_output2.csv")
```

# Additional Information Request

-   Distribution of R squared, its average value and standard deviation

```{r}
est_output %>% 
  ggplot(aes(x = Reg2_ARS))+
  geom_density() + 
  xlab("Adjusted R Squared") +
  ggtitle("Dual Beta Model Adjusted R Squared Distribution")
```

*Average value and standard deviation of Adjusted R Squared*

```{r}
output_stat <- est_output %>% 
  skim() %>% 
  mutate_if(is.numeric, round, digits = 4) %>% 
  filter(skim_variable != "PERMNO")

output_stat %<>% select(-c(n_missing, complete_rate))
```

**Run the VIFs for each of the two parameters**

```{r}
var_inf <- estimation %>% 
  nest(data=-PERMNO) %>% 
  mutate(model = map(data, ~lm(excess_ret ~ mket_prem + sector_prem, data =.)),
        vf_stat = map(model,vif)) %>% 
  unnest(vf_stat)

vector_name <- rep(c("Reg2_VF1","Reg2_VF2"), 357)

# Bind vector_name and var_inf together

var_inf <- tibble(cbind(var_inf, vector_name))

# Remove columns and modify column name

var_inf %<>% 
  spread(key = vector_name, value = vf_stat) %>% 
  mutate(PERMNO = as.factor(PERMNO)) %>% 
  select(PERMNO, Reg2_VF1, Reg2_VF2)
```

```{r}
est_output_modified <- sqldf("SELECT e.*, v.Reg2_VF1,v.Reg2_VF2
                             FROM est_output as e
                             JOIN var_inf as v
                             ON e.PERMNO = v.PERMNO") %>% as.tibble()
```

```{r}
est_output_modified %<>% mutate(PERMNO = as.factor(PERMNO),
                               Sector = as.factor(Sector))
est_output_modified %>% ggplot(aes(x = Sector,  y = Reg2_VF1))+
  geom_boxplot() +
  coord_flip() + 
  ggtitle(" Dual Beta Model Variance Inflation Factor of Sectors") +
  ylab("Variance Inflation Factor")
```

# Run a Regression with Beta 2 as explanatory variable only

-   fit_stat 3 will include the alphas, betas, and their corresponding p values

```{r}

fit_stat3 <- estimation %>% 
  nest(data = -PERMNO) %>% 
  mutate(model = map(data, ~lm(excess_ret ~ sector_prem, data=.)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied)

```

-   fit_stat 4 will include the model's adjusted R squared and its p value

```{r}

fit_stat4 <- estimation %>% 
  nest(data = -PERMNO) %>% 
  mutate(model = map(data,~lm(excess_ret ~ sector_prem, data =.)),
         tidied = map(model, glance)) %>% 
  unnest(tidied)

```

-   Round the output by 4 decimal places and remove some unnecessary columns

```{r}
fit_stat3 %<>% mutate_if(is.numeric, round, digits = 4)
fit_stat3 %<>% select(-c(data, model, std.error, statistic)) 
```

```{r}
fit_stat4 %<>% mutate_if(is.numeric, round, digits = 4)
fit_stat4 %<>% select(PERMNO, adj.r.squared, p.value)
```

Join two outputs together

```{r}
est_output3 <- join(fit_stat3, fit_stat4, by = "PERMNO")
est_output3[,6] <- NULL #Remove the Null column
```

*Plot Statistic outputs*

```{r}
est_output3 %>% 
  ggplot() +
  geom_density(aes(x = estimate, col = term), data = est_output3) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta2")) + 
  theme(panel.background = element_blank()) +
  xlab("Coefficient") + 
  ylab("Density") +
  ggtitle("Distribution of Coefficients of Alpha and Beta2")
```

```{r}
est_output3 %>% ggplot() +
  geom_density(aes(x = p.value, col = term), data = est_output3) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta2")) + 
  theme(panel.background = element_blank()) +
  xlab("P-Value") + 
  ylab("Density") +
  ggtitle("P-Value of Alpha and Beta2 Distribution")
```

```{r}
est_output3 %>% ggplot() +
  geom_point(aes(y= p.value, x = PERMNO, col = term), data = est_output3, alpha = 0.8) + 
  scale_color_discrete(guide = guide_legend(title = "Variable"), labels = c("Alpha","Beta2")) + 
  theme(panel.background = element_blank(),
        legend.key = element_blank()) +
  xlab("PERMNO") + 
  ylab("P-Value") +
  ggtitle("Beta2 Model Distribution of Coefficient's P-Value")
```

Modified table output

```{r}
est_output3 %<>% mutate(Alpha = NA, 
                       Beta2 = NA, 
                       Alpha_pval = NA,
                       Beta2_pval = NA,
                       PERMNO = as.factor(PERMNO)) %>% as.tibble()

# Fill variable Alpha 
for (i in 2:nrow(est_output3)){
  est_output3$Alpha[i] = with(est_output3,ifelse(PERMNO[i]==PERMNO[i-1], estimate[i-1], NA))
}

# Fill variable Beta

for (i in 2:nrow(est_output3)){
  est_output3$Beta2[i] = with(est_output3,
                             ifelse(PERMNO[i] == PERMNO[i-1],
                                    estimate[i], NA))
}

# Fill variable Beta2_pval 

for (i in 2:nrow(est_output3)){
  est_output3$Beta2_pval[i] = with(est_output3,
                             ifelse(PERMNO[i] == PERMNO[i-1],
                                    p.value[i], NA))}
  
# Fill variable Alpha_pval

for (i in 2:nrow(est_output3)){
  est_output3$Alpha_pval[i] = with(est_output3,
                             ifelse(PERMNO[i] == PERMNO[i-1],
                                    p.value[i-1], NA))}


est_output3 %<>% 
  filter(term != "(Intercept)") %>% 
  select(-c(term, estimate, p.value))

# Rename some columns and rows

est_output3 %<>% 
  dplyr::rename( 
      Reg3_ARS = adj.r.squared, 
      Reg3_B0 = Alpha,
      Reg3_B2 = Beta2,
      Reg3_P0 = Alpha_pval,
      Reg3_P2 = Beta2_pval)

```

*Plot adjusted R squared*

```{r}
est_output3 %>% 
  ggplot(aes(x = Reg3_ARS))+
  geom_density() + 
  xlab("Adjusted R Squared") +
  ggtitle("Beta2 Model Adjusted R Squared Distribution")
```

```{r}
est_output3 %>% skim() %>% select(-c(n_missing, complete_rate)) %>% mutate_if(is.numeric, round, digits = 4)
```

Export the file

```{r}
est_output3 <- sqldf("SELECT e.*, m.Sector, m.tic
                     FROM est_output3 as e
                     JOIN est_output as m
                     ON e.PERMNO = m.PERMNO") %>% as.tibble()
est_output3 %<>% select(PERMNO, tic, Sector, everything())
write.csv(est_output3,"beta2_model.csv")
```


# Regression 4 

```{r}
reg4 <- estimation %>% dplyr::rename(
  stock_mktcap = MKT_CAP,
  weighted_stock = MKTCAP_SHARE,
  weighted_return_stock = Return_Weighted,
) %>%
  select(
    date,
    year,
    PERMNO,
    TICKER,
    COMNAM,
    Sector,
    PRC,
    SHROUT,
    stock_mktcap,
    Sector_MKTCAP,
    ind_ret,
    EFFR,
    weighted_stock,
    weighted_return_stock,
    Daily_Sector_Return,
    excess_ret
  ) %>% as.tibble()
```


Daily Market Cap of each Sector


```{r}
sector_data <- reg4 %>% select(date, Sector,Sector_MKTCAP, Daily_Sector_Return) %>% unique() 
```

```{r}
# Create daily market cap data for all sector 

sector_mktcap_data<- sqldf("SELECT *, 
      sum(Sector_MKTCAP) over(partition by date) as total_mktcap
      from sector_data") %>% as.tibble()
```





1. Exclude financials sector

```{r}

# Create daily market cap data for all sector 

sector_mktcap_data<- sqldf("SELECT *, 
      sum(Sector_MKTCAP) over(partition by date) as total_mktcap
      from sector_data") %>% as.tibble()

# Create adjusted market cap data for all sectors, except the excluded one

adj_mktcap_data <-
  sector_mktcap_data %>%  filter(Sector != "Financials")

# Calculate the weight of each sector and the adjusted sector return based on the adjusted market cap

sector_ret_weighted <-
  sqldf(
    "select *, sum(Sector_MKTCAP) over (partition by date) as adj_mktcap
      from adj_mktcap_data"
  ) %T>%  as.tibble() %>% mutate(
    sector_weight = Sector_MKTCAP / adj_mktcap,
    sector_ret_weighted = Daily_Sector_Return * sector_weight
  ) 

# Calculat the adjusted market return
mkt_weighted_ret <-
  sqldf(
    "select *, sum(sector_ret_weighted) over (partition by date) as adj_mkt_ret
from sector_ret_weighted
                          "
  ) 
# Join with the stock data 

adjusted_mkt_data <- sqldf("select r.*,m.adj_mkt_ret
      from reg4 as r
      join mkt_weighted_ret as m
      on r.date = m.date
      and r.Sector = m.Sector") %T>% as.tibble() %>% mutate(mket_prem = adj_mkt_ret - EFFR)

adjusted_mkt_data %>% nest(data = -PERMNO) %>% mutate(
 model = map(data, ~lm(excess_ret ~ mket_prem, data =.)), 
      tidied = map(model, tidy)) %>% 
 unnest(tidied)

adjusted_mkt_data %>% nest(data = -PERMNO) %>% mutate(
 model = map(data, ~lm(excess_ret ~ mket_prem, data =.)), 
      tidied = map(model, glance)) %>% 
 unnest(tidied)
```

Create a vector of all sectors to be used later

```{r}
sector_vector <-
  c(
    "Financials",
    "Industrials",
    "Consumer Discretionary",
    "Information Technology",
    "Health Care",
    "Consumer Staples",
    "Utilities",
    "Materials",
    "Real Estate",
    "Energy",
    "Consumer Services"
  )
```

```{r}
tic("Time consumed: ")
for (i in sector_vector){
  adj_mktcap_data <-
  sector_mktcap_data %>%  filter(Sector != i)

# Calculate the weight of each sector and the adjusted sector return based on the adjusted market cap
  
sector_ret_weighted <-
  sqldf(
    "select *, sum(Sector_MKTCAP) over (partition by date) as adj_mktcap
      from adj_mktcap_data"
  ) %T>%  as.tibble() %>% mutate(
    sector_weight = Sector_MKTCAP / adj_mktcap,
    sector_ret_weighted = Daily_Sector_Return * sector_weight
  ) 

# Calculate the adjusted market return
mkt_weighted_ret <-
  sqldf(
    "select *, sum(sector_ret_weighted) over (partition by date) as adj_mkt_ret
from sector_ret_weighted"
  ) 

# Join with the stock data 

adjusted_mkt_data <- sqldf("select r.*,m.adj_mkt_ret
      from reg4 as r
      join mkt_weighted_ret as m
      on r.date = m.date
      and r.Sector = m.Sector") %T>% as.tibble() %>% mutate(mket_prem = adj_mkt_ret - EFFR)

# Create name of vector to store function 
fit_stat1_reg4 <- adjusted_mkt_data %>% nest(data = -PERMNO) %>% mutate(
 model = map(data, ~lm(excess_ret ~ mket_prem, data =.)), 
      tidied = map(model, tidy)) %>% 
 unnest(tidied)

assign(paste0("fit_stat1_exclude_",i), fit_stat1_reg4)

fit_stat2_reg4 <- adjusted_mkt_data %>% nest(data = -PERMNO) %>% mutate(
 model = map(data, ~lm(excess_ret ~ mket_prem, data =.)), 
      tidied = map(model, glance)) %>% 
 unnest(tidied)

assign(paste0("fit_stat2_exclude_",i), fit_stat2_reg4)

}

toc()

```

Now gather the the output

```{r}
# Gather output for stat1 first

## Create a function to filter only necessary output from stat1 
stat1_filter <- function(input){
  input %<>%
    select(PERMNO, term, estimate, p.value) %>% 
    mutate_if(is.numeric, round, digits = 4)
  return(input)
}

#1
fit_stat1_exclude_Consumer_Discretionary <- stat1_filter(`fit_stat1_exclude_Consumer Discretionary`)

#2 

fit_stat1_exclude_Consumer_Services <- stat1_filter(`fit_stat1_exclude_Consumer Services`)

#3

fit_stat1_exclude_Consumer_Staples <- stat1_filter(`fit_stat1_exclude_Consumer Staples`)

#4

fit_stat1_exclude_Energy <- stat1_filter(`fit_stat1_exclude_Health Care`)

#5

fit_stat1_exclude_Health_Care <- stat1_filter(`fit_stat1_exclude_Health Care`)

#6

fit_stat1_exclude_Financials <- stat1_filter(fit_stat1_exclude_Financials)

#7

fit_stat1_exclude_Industrials <- stat1_filter(fit_stat1_exclude_Industrials)

#8

fit_stat1_exclude_Information_Technology <- stat1_filter(`fit_stat1_exclude_Information Technology`)

#9

fit_stat1_exclude_Real_Estate <- stat1_filter(`fit_stat1_exclude_Real Estate`)

#10

fit_stat1_exclude_Materials <- stat1_filter(fit_stat1_exclude_Materials)

#11

fit_stat1_exclude_Utilities <- stat1_filter(fit_stat1_exclude_Utilities)

```


```{r}
# Gather output for stat2

stat2_filter <- function(input){
  input %<>% 
    select(PERMNO, Reg4_ARS = adj.r.squared) %>% 
    mutate_if(is.numeric, round, digits = 4)
  return(input)
}

#1
fit_stat2_exclude_Consumer_Discretionary <- stat2_filter(`fit_stat2_exclude_Consumer Discretionary`)

#2 

fit_stat2_exclude_Consumer_Services <- stat2_filter(`fit_stat2_exclude_Consumer Services`)

#3

fit_stat2_exclude_Consumer_Staples <- stat2_filter(`fit_stat2_exclude_Consumer Staples`)

#4

fit_stat2_exclude_Energy <- stat2_filter(`fit_stat2_exclude_Health Care`)

#5

fit_stat2_exclude_Health_Care <- stat2_filter(`fit_stat2_exclude_Health Care`)

#6

fit_stat2_exclude_Financials <- stat2_filter(fit_stat2_exclude_Financials)

#7

fit_stat2_exclude_Industrials <- stat2_filter(fit_stat2_exclude_Industrials)

#8

fit_stat2_exclude_Information_Technology <- stat2_filter(`fit_stat2_exclude_Information Technology`)

#9

fit_stat2_exclude_Real_Estate <- stat2_filter(`fit_stat2_exclude_Real Estate`)

#10

fit_stat2_exclude_Materials <- stat2_filter(fit_stat2_exclude_Materials)

#11

fit_stat2_exclude_Utilities <- stat2_filter(fit_stat2_exclude_Utilities)

```

Restructure fit_stat1

```{r}
restructure <- function(input){
  input %<>% mutate(Reg4_B0 = NA,
                   Reg4_B1 = NA,
                   Reg4_P1 = NA,
                   Reg4_P0 = NA)
  for (i in 2:nrow(input)){
    input$Reg4_B0[i] <- with(input, ifelse(PERMNO[i] == PERMNO[i-1], estimate[i-1], NA))
    input$Reg4_B1[i] <- with(input, ifelse(PERMNO[i] == PERMNO[i-1], estimate[i], NA))
    input$Reg4_P0[i] <- with(input, ifelse(PERMNO[i] == PERMNO[i-1], p.value[i-1], NA))
    input$Reg4_P1[i] <- with(input, ifelse(PERMNO[i] == PERMNO[i-1], p.value[i], NA))
  }
  input %<>% filter(term != "(Intercept)") %>% select(PERMNO, Reg4_B0, Reg4_B1, Reg4_P0, Reg4_P1)
  
  return(input)
}

# 1
fit_stat1_exclude_Consumer_Discretionary <-  restructure(fit_stat1_exclude_Consumer_Discretionary)

# 2
fit_stat1_exclude_Consumer_Services <-  restructure(fit_stat1_exclude_Consumer_Services)

# 3
fit_stat1_exclude_Consumer_Staples <-  restructure(fit_stat1_exclude_Consumer_Staples)

# 4
fit_stat1_exclude_Financials <-  restructure(fit_stat1_exclude_Financials)

# 5
fit_stat1_exclude_Health_Care <-  restructure(fit_stat1_exclude_Health_Care)

# 6
fit_stat1_exclude_Industrials <-  restructure(fit_stat1_exclude_Industrials)

# 7
fit_stat1_exclude_Information_Technology <-  restructure(fit_stat1_exclude_Information_Technology)

# 8
fit_stat1_exclude_Materials <-  restructure(fit_stat1_exclude_Materials)

#9
fit_stat1_exclude_Real_Estate <-  restructure(fit_stat1_exclude_Real_Estate)

#10
fit_stat1_exclude_Energy <-  restructure(fit_stat1_exclude_Energy)

#11
fit_stat1_exclude_Utilities <-  restructure(fit_stat1_exclude_Utilities)
```

Restructure fit_stat2

```{r}
#1
mk_excluded_consumer_discretionary <- join(fit_stat1_exclude_Consumer_Discretionary, fit_stat2_exclude_Consumer_Discretionary, by = "PERMNO")

#2
mk_excluded_consumer_service <- join(fit_stat1_exclude_Consumer_Services, fit_stat2_exclude_Consumer_Services, by = "PERMNO")

#3
mk_excluded_staples <- join(fit_stat1_exclude_Consumer_Staples, fit_stat2_exclude_Consumer_Staples, by = "PERMNO")

#4
mk_excluded_health_care<- join(fit_stat1_exclude_Health_Care, fit_stat2_exclude_Health_Care, by = "PERMNO")

#5
mk_excluded_financials <- join(fit_stat1_exclude_Financials, fit_stat2_exclude_Financials, by = "PERMNO")

#6
mk_excluded_consumer_industrials <- join(fit_stat1_exclude_Industrials, fit_stat2_exclude_Industrials, by = "PERMNO")

#7
mk_excluded_information_tech <- join(fit_stat1_exclude_Information_Technology, fit_stat2_exclude_Information_Technology, by = "PERMNO")

#8
mk_excluded_real_estate <- join(fit_stat1_exclude_Real_Estate, fit_stat2_exclude_Real_Estate, by = "PERMNO")

#9
mk_excluded_utilities <- join(fit_stat1_exclude_Utilities, fit_stat2_exclude_Utilities, by = "PERMNO")

#10
mk_excluded_materials <- join(fit_stat1_exclude_Materials, fit_stat2_exclude_Materials, by = "PERMNO")

#11
mk_excluded_energy<- join(fit_stat1_exclude_Energy, fit_stat2_exclude_Energy, by = "PERMNO")

```


join with the previous output to include tic and Sector 

```{r}
#Create a loop 

output_list <- list(mk_excluded_consumer_discretionary = mk_excluded_consumer_discretionary, 
                    mk_excluded_consumer_industrials = mk_excluded_consumer_industrials,
                    mk_excluded_consumer_service = mk_excluded_consumer_service,
                    mk_excluded_energy = mk_excluded_energy,
                    mk_excluded_financials = mk_excluded_financials,
                    mk_excluded_health_care = mk_excluded_health_care,
                    mk_excluded_information_tech = mk_excluded_information_tech,
                    mk_excluded_materials = mk_excluded_materials,
                    mk_excluded_real_estate = mk_excluded_real_estate,
                    mk_excluded_staples = mk_excluded_staples,
                    mk_excluded_utilities = mk_excluded_utilities)

name_list <-  c("mk_excluded_consumer_discretionary", 
                    "mk_excluded_industrials",
                    "mk_excluded_consumer_service",
                    "mk_excluded_energy",
                    "mk_excluded_financials",
                    "mk_excluded_health_care",
                    "mk_excluded_information_tech",
                    "mk_excluded_materials",
                    "mk_excluded_real_estate",
                    "mk_excluded_staples",
                    "mk_excluded_utilities")


suplement_tic <- function(input) {
  input %<>% join(est_output3 %>% select(PERMNO, tic, Sector), by = "PERMNO") %>%        select(PERMNO, tic, Sector, everything())
  return(input)
}

for (i in 1:length(output_list)){
  a <- suplement_tic(output_list[[i]]) 
  assign(name_list[i], a)
}

```
 
 
# Create requested statistic
```{r}
for (i in 1:length(output_list)){
  a <- output_list[[i]] %>% describe() %>%
    select(n, mean, sd, min, max, kurtosis, se) %>% 
    mutate_if(is.numeric, round, digits = 4)
  assign(paste0("additional_stat_",name_list[i]), a)
}
```
 
# Export the output

```{r}
#1
write.csv(additional_stat_mk_excluded_consumer_discretionary,"mk_excluded_consumer_discretionary.csv")

#2
write.csv(additional_stat_mk_excluded_industrials, "mk_excluded_industrials.csv")

#3
write.csv(additional_stat_mk_excluded_consumer_service,"mk_excluded_consumer_service.csv"
          )

#4
write.csv(additional_stat_mk_excluded_energy, "mk_excluded_energy.csv")

#5
write.csv(additional_stat_mk_excluded_financials, "mk_excluded_financials.csv")

#6
write.csv(additional_stat_mk_excluded_health_care, "mk_excluded_health_care.csv")

#7
write.csv(additional_stat_mk_excluded_information_tech,"mk_excluded_information_tech.csv")

#8
write.csv(additional_stat_mk_excluded_materials, "mk_excluded_materials.csv")

#9
write.csv(additional_stat_mk_excluded_real_estate, "mk_excluded_real_estate.csv")

#10
write.csv(additional_stat_mk_excluded_staples, "mk_excluded_staples.csv")

#11
write.csv(additional_stat_mk_excluded_utilities,"mk_excluded_utilities.csv")
```

```{r}
# Calculate the daily adjusted return for the market for each sector 

x <- sector_ret_weighted
x$new_ret_adj <- NA
x <- x %>% mutate(ret_x_mktcap = Daily_Sector_Return * Sector_MKTCAP)
for (i in 1:nrow(x)) {
  x$new_ret_adj[i] <-
    (1 / (x$total_mktcap[i] - x$Sector_MKTCAP[i])) * (
      x %>% filter(Sector != Sector[i] &
                     date == date[i]) %>% dplyr::group_by(date) %>%
        dplyr::summarize(adj_mkt_ret = sum(ret_x_mktcap))
    )[1, 'adj_mkt_ret']
}

```

```{r}
# Calculate the adjusted return of the sector for each stock 
## cmt these out to avoid long time processing

# y = adjusted_mkt_data
# 
# y$new_ind_ret_adj <- NA
# 
# tic("time consumed")
# for (i in 1:nrow(y)){
#   y$new_ind_ret_adj[i] <- 
#     (1/(y$Sector_MKTCAP[i] - y$stock_mktcap[i]))*(y %>% 
#                                                     filter(TICKER != TICKER[i] & date == date[i] & Sector == Sector[i]) %>% 
#                                                     mutate(ind_ret_x_mktcap = 
#                                                              ind_ret*stock_mktcap) %>% 
#                                                     dplyr::group_by(date) %>% 
#                                                     dplyr::summarize(adj_stock_ret = sum(ind_ret_x_mktcap)))[1,'adj_stock_ret']
# }
# toc()
# 
# y$new_ind_ret_adj <- as.numeric(y$new_ind_ret_adj)
# x$new_ret_adj <- as.numeric(x$new_ret_adj)
# 
# 
# write.csv(y, 'reg5_data.csv')

```

Join data x with y to to add sector adjusted return for x
 
```{r}
y <- read.csv('reg5_data.csv', stringsAsFactors = T) %>% as.tibble()

y %<>% mutate(date = ymd(date))

x2 <- x %>% select(date, Sector, mkt_adj_sector_ret = new_ret_adj)



data_reg5 <-
  inner_join(x2, y, by = c('date', 'Sector')) %>% select(
    date,
    Sector,
    PERMNO,
    tic = TICKER,
    mkt_adj_sector_ret,
    sector_adj_ret = new_ind_ret_adj,
    effr = EFFR,
    excess_ret
  )

data_reg5 %<>% mutate(mkt_adj_sector_ret = as.numeric(mkt_adj_sector_ret),
                      mket_prem = mkt_adj_sector_ret - effr,
                     sector_prem = sector_adj_ret - effr)

```

# Run Regression 5

```{r}
# reg5_fit1 contains coefficients of alpha, beta1, and beta2 
reg5_fit1 <- data_reg5 %>% 
  nest(data = -PERMNO) %>% 
  mutate(model = map(data, ~lm(excess_ret ~ mket_prem + sector_prem, data =.)), 
      tidied = map(model, tidy)) %>% 
 unnest(tidied)

# reg5_fit2 contains the model' p-values
reg5_fit2 <- data_reg5 %>% nest(data = -PERMNO) %>% 
  mutate(
 model = map(data, ~lm(excess_ret ~ mket_prem + sector_prem, data =.)), 
      tidied = map(model, glance)) %>% 
 unnest(tidied)
```

Summarize output 

```{r}
# round outputs by 4 decimal places
round_output <- function(input){
  input %<>% mutate_if(is.numeric, round, digits = 4)
  return(input)
}
reg5_fit1 <- round_output(reg5_fit1)
reg5_fit2 <- round_output(reg5_fit2)

# remove unnecessary columns and join 2 stats together

reg5_fit1 %<>% select(PERMNO, term, estimate, p.value_fit1 = p.value)

reg5_fit2 %<>% select(PERMNO, adj.r.squared)

est_output_model5 <- inner_join(reg5_fit1, reg5_fit2, by = 'PERMNO')

# Reformat the table 

est_output_model5 %<>% mutate(Reg5_B0 = NA, 
                       Reg5_P0 = NA, 
                       Reg5_B1 = NA,
                       Reg5_P1 = NA,
                       Reg5_B2 = NA,
                       Reg5_P2 = NA) %>%
                      as.tibble()
```

Reformat output table

```{r}
g <- est_output_model5$PERMNO

for (i in 2:(nrow(est_output_model5)-1)){
  for (j in 6:11){
    if ((g[i] == g[i-1]) & (g[i] == g[i+1])){
      if (j == 6) {
        est_output_model5[i,j] = est_output_model5$estimate[i-1]
      } else if (j == 7){
        est_output_model5[i,j] = est_output_model5$p.value_fit1[i-1]
      } else if (j == 8) {
        est_output_model5[i,j] = est_output_model5$estimate[i]
      } else if (j == 9) {
        est_output_model5[i,j] = est_output_model5$p.value_fit1[i]
      } else if (j == 10) {
        est_output_model5[i,j] = est_output_model5$estimate[i+1]
      } else if (j == 11) {
        est_output_model5[i,j] = est_output_model5$p.value_fit1[i+1]
      }
      else {
        NA
      }
    }
  }
}

est_output_model5 %<>% filter(complete.cases(.)) %>% select(-c(term, estimate, p.value_fit1, adj.r.squared))

est_output_model5 %<>% mutate(PERMNO = as.factor(PERMNO))

# Join with fit 2 to include adjusted r squared

est_output_model5 <- sqldf('SELECT e.*, f.`adj.r.squared` as Reg5_ARS
                            FROM est_output_model5 as e 
                            JOIN reg5_fit2 as f
                            on e.PERMNO = f.PERMNO')
```

Compute VIFs

```{r}
vif_reg5 <- data_reg5 %>% 
  nest(data=-PERMNO) %>% 
  mutate(model = map(data, ~lm(excess_ret ~ mket_prem + sector_prem, data =.)),
        vf_stat = map(model,vif)) %>% 
  unnest(vf_stat)

# Bind vector_name and vif_reg5 together
vector_name2 <- rep(c('Reg5_VF1', 'Reg5_VF2'), 357)

vif_reg5 <- tibble(cbind(vif_reg5, vector_name2))

# Remove columns and modify column name

vif_reg5 %<>% 
  spread(key = vector_name2, value = vf_stat) %>% 
  mutate(PERMNO = as.factor(PERMNO)) %>% 
  select(PERMNO, Reg5_VF1, Reg5_VF2)
```

Join all output together

```{r}
est_output_model5 <- inner_join(est_output_model5, vif_reg5, by = 'PERMNO')

est_output_model5 %<>% mutate_if(is.numeric, round, digits = 4)

additional_stat_reg5 <- (est_output_model5 %>% describe() %>% select(mean, median, sd, kurtosis))[c(-1:-3),]

additional_stat_reg5 %<>% mutate_if(is.numeric, round, digits = 4)
```

Add sector and ticker name

```{r}
est_output_model5 <- suplement_tic(est_output_model5)
```


Export regression 5 output

```{r}
write.csv(est_output_model5, 'reg5_output.csv')
write.csv(additional_stat_reg5, 'additional_stat_reg5.csv')
```


